---
title: "buoys"
author: "MA-615-415"
format: html
editor: visual
---

## The Buoys project

In the last class we looked at the [National Data Buoy Center](https://www.ndbc.noaa.gov/) and downloaded 1984 data from [Station 44013](https://www.ndbc.noaa.gov/station_page.php?station=44013).

Today we want to visualize this data and add more data from other years.

We will do this project slowly, step-by-step as we learn the essentials of the [Tidyverse](https://www.google.com/search?q=cran+r+tidyverse&rlz=1C1GCEU_enUS1148US1148&oq=cran+r+tidyverse&gs_lcrp=EgZjaHJvbWUyBggAEEUYOTIHCAEQIRiPAtIBCDY1NDdqMGo3qAIAsAIA&sourceid=chrome&ie=UTF-8) [[See also the Tidyverse website:](https://www.tidyverse.org/)] and Exploratory Data Analysis [see <a href="https://cran.r-project.org/doc/contrib/de_Jonge+van_der_Loo-Introduction_to_data_cleaning_with_R.pdf">
Introduction to data cleaning with R</a>].

## Data

In the last class, we downloaded data from the year 1984

```{r}
#| label: read station 44013 year 1984 

file_root <- "https://www.ndbc.noaa.gov/view_text_file.php?filename=44013h"
tail <- ".txt.gz&dir=data/historical/stdmet/"
    
path <- paste0(file_root,"1984",tail)

buoy <- read.table(path, fill = TRUE, header = TRUE, sep = "")


head(buoy)

# Let'slook at airtemp for 1984

nat <- which(is.na(buoy$ATMP))

nat <- length(nat)


```

Is there any NA data in the Air Temperture readings? 
`r as.logical(nat)`

```{r}
#| label: save data

airtemp <- buoy$ATMP

saveRDS(airtemp , file = "airtemp.rdata")

```


